Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-18 stp/paper_aaai/main.tex

Our goal is to take a set of graphs (the semantic models from the training set 
$S_T$) and find patterns that appear often across that set of graphs. This is 
known as the Frequent Subgraph Mining (FSM), which contains the subgraph 
isomorphism, known to be NP-complete. 
There exists a range of tools that can achieve this task using Transactional 
Frequent Graph Pattern Mining\cite{petermann2017dimspan,yan2002gspan}. 
We chose to use DIMSpan \cite{petermann2017dimspan}. 
\ddg{CHECK! How do they solve an NP-complete problem??}
\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}

>>>>

Our goal is to take a set of graphs (the semantic models from the training set 
$S_T$) and find patterns that appear often across that set of graphs. This is 
known as the Frequent Subgraph Mining (FSM), which contains the subgraph 
isomorphism, known to be NP-complete. 
There exists a range of tools that can achieve this task using Transactional 
Frequent Graph Pattern Mining \cite{petermann2017dimspan,yan2002gspan}.
We chose to use DIMSpan \cite{petermann2017dimspan}, which uses gSpan as a
pruning procedure \cite{yan2002gspan}.
%\ddg{CHECK! How do they solve an NP-complete problem??}
%\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}
